\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2020-03-11 popl-2019-journal-v/paper.tex
Point out in the outline that some sections are intended for experts.

\begin{jversion}
  This text is an extended version of a paper that was presented at POPL 2019~\citep{skorstengaard_stktokens_2019}.
  Compared to the earlier text, this version adds and explains aspects of our work that were left out in the conference version due to space restrictions.
  The added details include a better motivation of sealing (\sectionname~\ref{sec:purpose-sealing}), the requirements of well-formedness (\sectionname~\ref{sec:well-form-reas}) and reasonability of components (\sectionname~\ref{sec:reasonable-components}).
  The section on proving full-abstraction (\sectionname~\ref{sec:fa-proof}) has been rewritten to better explain the method used for the full-abstraction proof.
  This includes a description and motivation of the Kripke worlds (\sectionname~\ref{subsec:worlds}) and logical relation (\sectionname~\ref{subsec:logical-relation}) that we use to do this.
  This paper is accompanied by a technical report~\citep{technical_report_popl} with technical details and proofs.
\end{jversion}
% Notes on new contributions (based on the journal version environment):
% More details about the definition of the cap. machine (decoding/encoding functions)
% Well-formedness definitions
% Reasonability definition
% Expanded discussion section
% More detailed description of worlds and
%   the logical relation used

@@

\section{Constructing Worlds: Solving the Recursive Domain Equation}
\label{subsubsec:rec-dom-eq}
In the previous sections, we sketched what our worlds should be.
However, the worlds we want constitute a self-referential domain equation for which no solution exists in set and domain theory.
% Move to a different domain
Therefore, we need to move to a different domain with enough structure for a solution to exist for recursive equations.
Solutions to recursive domain equations can be found using standard techniques~\citep{scott_1976,america_1989,Birkedal:2011:SKM:1926385.1926401}.
Essentially, we move to a setting where instead of sets we have c.o.f.e.'s (complete ordered families of equivalences), instead of functions we have non-expansive functions, and instead of relations we have downwards-closed relations.
A c.o.f.e.\ can be thought of as a set with added structure.
Specifically, c.o.f.e.'s have a step-index that must satisfy a set of conditions which provide sufficient structure for a solution to exist for the recursive domain equation.

@@

\section{Related Work}
In this section, we discuss related work on securely enforcing control flow correctness and/or local state encapsulation or the linear capabilities we use to do it.
We do not repeat the work we discussed in Section~\ref{sec:introduction}.

>>>>

\begin{jversion}
  This text is an extended version of a paper that was presented at POPL 2019~\citep{skorstengaard_stktokens_2019}.
  Compared to the earlier text, this version adds and explains aspects of our work that were left out in the conference version due to space restrictions.
  The added details include a better motivation of sealing (\sectionname~\ref{sec:purpose-sealing}), the requirements of well-formedness (\sectionname~\ref{sec:well-form-reas}) and reasonability of components (\sectionname~\ref{sec:reasonable-components}).
  The section on proving full-abstraction (\sectionname~\ref{sec:fa-proof}) has been rewritten to better explain the method used for the full-abstraction proof.
  This includes a description and motivation of the Kripke worlds (\sectionname~\ref{subsec:worlds}) and logical relation (\sectionname~\ref{subsec:logical-relation}) that we use to do this.
  This paper is accompanied by a technical report~\citep{technical_report_popl} with technical details and proofs.

  Generally, we have only added material that we believe is valuable to some readers, and we have worked hard to explain the more technical material and make it digestible.
  Additionally, while Sections~\ref{sec:cap-mach-w-seal-and-lin}, \ref{sec:stktokens-explained},~\ref{sec:form-secur-with},~\ref{sec:discussion} and~\ref{sec:related-work} are intended for all readers, we have kept the more technical sections about the proof of full abstraction separate in Sections~\ref{sec:fa-proof} and~\ref{sec:rec-dom-eq}, so that it can be easily skipped by readers who prefer to skip those explanations.
\end{jversion}
% Notes on new contributions (based on the journal version environment):
% More details about the definition of the cap. machine (decoding/encoding functions)
% Well-formedness definitions
% Reasonability definition
% Expanded discussion section
% More detailed description of worlds and
%   the logical relation used

@@

\section{Constructing Worlds: Solving the Recursive Domain Equation}
\label{sec:rec-dom-eq}
In the previous sections, we sketched what our worlds should be.
However, the worlds we want constitute a self-referential domain equation for which no solution exists in set and domain theory.
% Move to a different domain
Therefore, we need to move to a different domain with enough structure for a solution to exist for recursive equations.
Solutions to recursive domain equations can be found using standard techniques~\citep{scott_1976,america_1989,Birkedal:2011:SKM:1926385.1926401}.
Essentially, we move to a setting where instead of sets we have c.o.f.e.'s (complete ordered families of equivalences), instead of functions we have non-expansive functions, and instead of relations we have downwards-closed relations.
A c.o.f.e.\ can be thought of as a set with added structure.
Specifically, c.o.f.e.'s have a step-index that must satisfy a set of conditions which provide sufficient structure for a solution to exist for the recursive domain equation.

@@

\section{Related Work}
\label{sec:related-work}
In this section, we discuss related work on securely enforcing control flow correctness and/or local state encapsulation or the linear capabilities we use to do it.
We do not repeat the work we discussed in Section~\ref{sec:introduction}.
